\documentclass{article}
\usepackage{graphicx} % Required for inserting images

\title{Problem Set 1}
\author{savannahjsimpson }
\date{January 2024}

\begin{document}

\maketitle

\section{Personal Summary}
My first real exposure to the field of data science took place last semester in the Statistics for Decision Making course. Throughout the semester, I often found myself struggling with certain concepts, but this frustration was closely followed with excitement and satisfaction once I was able to master a specific task. The experience offered in such a field is one that peaks my interest as it is ever evolving and requires problem solving. Throughout this course I aim to strengthen my data science analysis approaches and gain a more holistic understanding of the studied programs. I am most familiar with RSTudio as that is what was focused on in my previous course, but am looking forward to becoming more familiar with different programs. As for economic topics, I enjoy governmental relations to business and public economics. This semester I am planning to do research related to suggested tipping as this is (hopefully) my final semester. I would like to further explore this topic through the skills learned in this class. Post graduation, I am currently planning to gain experience in commercial banking, starting as a credit analyst. In the long run I would like to have a career that leans more into policy such as working with the Federal Reserve. 

\section{Equation}
\(a^2 + b^2 = c^2\)




\end{document}

